NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PE, PG and PS lipids

### 2017-08-23 Manuscript/manuscript.tex
Add table with simulated systems. Not ready yet.

>>>>

\section{Simulated systems}
\begin{table*}[!p]
%\begin{sidewaystable*}[!p]
\centering
\caption{List of MD simulations. The salt concentrations calculated as 
   [salt]=N$_{\rm c} \times$[water]\,/\,N$_{\rm w}$, where [water]\,=\,55.5~M.
%   these correspond the concentrations reported in the experiments by Akutsu et al.~\cite{akutsu81}.
%   The lipid force fields named as in our previous work~\cite{botan15}.
}\label{IONsystems}
\begin{minipage}[t]{\textwidth}
\begin{tabular}{l c c r r r r r r c c}
  %\hline
  % some footnotes are not visible in typeset-MS (pdf)
 lipid/counter-ions & force field for lipids / ions & NaCl (mM) & CaCl$_2$\,(mM) &  \footnote{Number of lipid molecules}N$_{\rm l}$   &  \footnote{Number of water molecules}N$_{\rm w}$   & \footnote{Number of additional cations}N$_{\rm c}$  & \footnote{Simulation temperature}T (K)  & \footnote{Total simulation time}t$_{{\rm sim}}$(ns) & \footnote{Time used for analysis}t$_{{\rm anal}}$ (ns) &   \footnote{Reference for simulation files}files\\
  \hline
  DPPE  & Slipids \cite{jambeck12b} &0 & 0        & 288 			   		& 9386 & 0  & 336  & 200 & 100 & \cite{slipidsDPPEfiles}  \\
    \hline
    DOPS/Na$^+$  & CHARMM36 \cite{??}  \todoi{Correct citation for CHARMM DOPS}      &0 & 0        & 128 			   		& 4480 & 0  & 303  & 500 & 100 & \cite{??}
    \todoi{By Piggot: http://nmrlipids.blogspot.com/2017/03/nmrlipids-iv-headgroup-glycerol.html?showComment=1491425687561\#c4932902612512697301. We need to decide the switching version or discuss this somehow.}  \\
    DOPS/Na$^+$  & CHARMM36ua \cite{??} \todoi{Correct citation for CHARMMua DOPS}        &0 & 0        & 128 			   		& 4480 & 0  & 303  & 500 & 100 & \cite{??}
    \todoi{Delivered by Piggot. We need to decide the switching version or discuss this somehow. Data to be uploaded in Zenodo?}  \\
    DOPS/Na$^+$  & Slipids \cite{jambeck13}        &0 & 0        & 128 			   		& 4480 & 0  & 303  & 500 & 100 & \cite{??}
    \todoi{Delivered by Piggot. We need to decide the cut-off version or discuss this somehow. Data to be uploaded in Zenodo?}  \\
    DOPS/Na$^+$  & Slipids \cite{jambeck13}        &0 & 0        & 288 			   		& 11232 & 0  & 303  & 200 & 100 & \cite{slipidsDOPSfiles} \\
    DOPS/Na$^+$  & Berger \cite{mukhopadhyay04}        &0 & 0        & 128 			   		& 4480 & 0  & 303  & 500 & 100 & \cite{??}
    \todoi{Delivered by Piggot. Data to be uploaded in Zenodo?}  \\
    DOPS/Na$^+$  & GROMOS-CKP \cite{??} \todoi{Correct citation(s) for CKP.}       &0 & 0        & 128 			   		& 4480 & 0  & 303  & 500 & 100 & \cite{??}
    \todoi{Delivered by Piggot. We need to decide between RF and PME or discuss this somehow. Data to be uploaded in Zenodo?}  \\
\end{tabular}
\end{minipage}
%\end{sidewaystable*} 
\end{table*}
